Some Fancy Title

### 2023-09-19 output/paper/manuscript.tex
Nothing.

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, breakable, enhanced]}{\end{tcolorbox}}\fi
